Streaming Slot-Value Extraction for Wikipedia Entities at Web-Scale

### 2013-11-06 paper/flairs27/content/discussion.tex

When we evaluate the results of slot extraction, we find three kinds of problems for accuracy: 1) wrong entities found; 2) wrong tags by the Lingpipe; 3) wrong results matched by the patterns.  We also have 
recall problems: 1) not enough good alias names to find all the entities. 2) not enough and powerful patterns to capture all the slot values. We will use entity resolution methods and other advanced methods to improve 
the accuracy and recall of entity extraction part.

@@

About 50\% of twitter entities are not found by the system. One reason is those entities are not popular. For example, a `Brenda Weiler' Google search result has 860,000 documents over the whole web. For our small portion of the web it might make sense. The histogram of the entities shows that more than half of the entities have appeared in less than 10 StreamItems. A good portion have appeared only once.

@@

Alltogether, We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us. We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself. On twitter entities we extract aliases manually as it is part of the rule of the KBA track. We process documents that mention entities for slot value extraction. Slot values are determined using pattern matching over coreferences of entities in sentences. Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

@@

>>>>

As part of future work regarding enhancing precision, we can focus on fixing the wrong entities found, remove noisy tags by the Lingpipe or use more accurate NLP taggers such as Stanford NLP (Due to the fact that Stanford NLP is very slow we avoided using it, as due to speed its use was out of question) and finally use better patterns to enahnce results matched by the patterns.  On the other hand to increase recall we need to find better aliases and go for more resources to discover other ways that an entity might be addressed (e.g. twitter id, website, etc), add powerful patterns that can capture more cases of slot values. We would also use entity resolution methods and other advanced methods to improve 
the accuracy and recall of entity extraction part.

@@

Some of the entities are not popular. For example, a `Brenda Weiler' Google search result has 860,000 documents over the whole web. For our small portion of the web it might make sense. The histogram of the entities shows that more than half of the entities have appeared in less than 10 StreamItems. A good portion have appeared only once.

@@

Alltogether, We experimented through different tools and approaches to best process the massive amounts of data on the platform that we had available to us. We generate aliases for wikipedia entities using Wiki API and extract some aliases from wikipedia pages text itself. We process documents that mention entities for slot value extraction. Slot values are determined using pattern matching over coreferences of entities in sentences. Finally post processing will filter, cleanup and infers some new slot values to enhance recall and accuracy.

@@

We sampled documents from the training data period to generate an initial set of patterns. We then use these patterns to generate  results. By manully looking at these results, we prune some patterns with poor ­performance and add more patterns that we identified from these results. We use several iterations to find the best patterns. We found that it is very time consuming to identity quality patterns.
